Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Mention not having to recompile application with RapidGL
Mention name of RapidGL

At the highest level is a library providing a simple render graph that can be
used to rapidly prototype OpenGL applications.  Similar to SVG, or Scalable
Vector Graphics, the render graph can be written in XML so scenes can easily be
saved, reloaded, and shared.

>>>>

At the highest level is a library named {\em RapidGL} providing a simple render
graph that can be used to rapidly prototype OpenGL applications.  Similar to
SVG, or Scalable Vector Graphics, the render graph can be written in XML so
scenes can easily be saved, reloaded, and shared.  In addition, users are free
to experiment with their scenes without ever recompiling the application.
